Volunteers in NESTA experiment \\linebreak  Technical Report

### 2023-12-18 volunteers/reportVolunteers.Rmd
added volunteers

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(kableExtra)
library(viridis)
library(rethinking)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(GGally)
library(dagitty)
library(reshape)
library(lubridate)
library(formatR)
library(ggrepel)

@@

```{r volunteersVis,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
volunteersLong <- read_csv(file = "nestaVolunteers/volunteersLong.csv")
competitionModel<- readRDS( "nestaVolunteers/competitionModel.rds")
volunteersJoint <- readRDS( file = "nestaVolunteers/datasets/volunteersJoint.rds")

>>>>

#libraries used
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(kableExtra)
library(viridis)
library(rethinking)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(GGally)
library(dagitty)
library(reshape)
library(lubridate)
library(formatR)
library(ggrepel)
library(rstan)

@@

```{r volunteersVis,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
volunteersLong <- read_csv(file = "data/volunteersLong.csv")
competitionModel<- readRDS( "models/competitionModel.rds")
volunteersJoint <- readRDS( file = "data/volunteersJoint.rds")
